---
title: "Real_data_experiments"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Real_data_experiments}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Set up

```{r setup, include = FALSE}
library(DS23IRLS)
library(msme)
library(dplyr)
library(ggplot2)
library(reshape2)
library(patchwork)
library(splitTools)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = '#>'
)
```

# Data sets

All three data sets come from the UCI Repository and are widely known in the ML community. For more details we advise to read the documentation under `?raisin` for raisin dataset. These data sets don't contain any missing, or categorical values, so only preprocessing needed is the removal of co-linear features, which will be detected via Pearson's Correlation.

```{r data sets}
data('raisin')
data('occupancy')
data('banknote')
knitr::kable(head(raisin))
knitr::kable(head(occupancy))
knitr::kable(head(banknote))
```

## Removing col-linear variables

```{r fig.width = 28, fig.height = 7}
cor_raisin    <- melt(round(cor(select(raisin, Area, MajorAxisLength, 
                                       MinorAxisLength, Eccentricity, 
                                       ConvexArea, Extent, Perimeter)), 2))
cor_occupancy <- melt(round(cor(select(occupancy, Temperature, Humidity, 
                                       Light, CO2, HumidityRatio)), 2))
cor_banknote  <- melt(round(cor(select(banknote, X1, X2, X3, X4)), 2))

plot_heatmaps(cor_raisin, cor_occupancy, cor_banknote)
```

As we can see, Raisin dataset has the abundance of highly correlated features.

```{r fig.width = 28, fig.height = 7, warning = FALSE}
raisin    <- raisin[, -c(1, 2, 3, 5)]
occupancy <- occupancy[, -5]
banknote  <- banknote[, -3]

cor_raisin    <- melt(round(cor(select(raisin, Eccentricity, 
                                       Extent, Perimeter)), 2))
cor_occupancy <- melt(round(cor(select(occupancy, Temperature, Humidity, 
                                       Light, CO2)), 2))
cor_banknote  <- melt(round(cor(select(banknote, X1, X2, X4)), 2))

plot_heatmaps(cor_raisin, cor_occupancy, cor_banknote)
```

After removing the highly correlated values (r rank \> 0.7) we've greatly diminished a Raisin dataset to just three out of seven variables, the occupancy dataset remained as it was, whereas from the banknote we removed X3 feature.

## Train test split

We prepare a train test split from our function which is a wrapper for the split function from `SplitTools`.

```{r}
raisin_split    <- train_test_split(raisin, p = c(0.2, 0.8))
occupancy_split <- train_test_split(occupancy, p = c(0.2, 0.8))
banknote_split  <- train_test_split(banknote, p = c(0.2, 0.8))
```

# Experiments

## Singular run

```{r}

```
